From Nested Virtualization Architecture \\To 2D Security Management for Distributed Clouds

### 2014-03-26 paper/draft.tex
updated paper.

The adoption of an extra layer of virtualization is capable to introduce a remarkable set of new features but it does not reduce the dimension of Trusted Code Base (TCB).
MH could represent a new approach to improve the potential benefits provided by the adoption of nested virtualization. In the following subsections, it will presented the four possible architectures achievable ``nesting'' of GPH and MH, underlying potentialities, drawbacks and potential cost of implementation.

>>>>

\noindent The adoption of an extra layer of virtualization is capable to introduce a remarkable set of new features but it does not reduce the dimension of Trusted Code Base (TCB).
MH could represent a new approach to improve the potential benefits provided by the adoption of nested virtualization. In the following subsections, it will presented the four possible architectures achievable ``nesting'' of GPH and MH, underlying potentialities, drawbacks and potential cost of implementation.
